---
title: "Homework 5 Solutions"
author: Meghan Bellerose
date: November 7, 2020
output: github_document
---

```{r, echo = FALSE}
library(tidyverse)
library(purrr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

The data for this problem were compiled by _The Washington Post_ and include information on more than 52,000 criminal homicides that occurred over the past decade in 50 major U.S. cities. 

```{r}
homicides = 
  read_csv("./hom_data/homicide_data.csv")
```

The dataset contains `r nrow(homicides)` rows and `r ncol(homicides)` columns, with each row representing a single homicide. The variables are location of a homicide (latitude and longitude), whether an arrest was made, and demographic information about the victim. 

The following code chunks create a `city_state` variable and provides a table of the number of unresolved homicides and total number of homicides by city.

```{r}
homicides_city = 
  homicides %>% 
  unite("city_state", city:state, sep = ", ", remove = TRUE)
```

# Probelem 2

This problem uses data from a longitudunal study with a control and experimental arm.

First, I'll create a tidy dataframe with the participants' subject IDs, study arms, and observations over time. 

```{r}
study_df = 
  list.files("./data")
```

Use purrr:map and save each result as new variable in dataframe 

# Problem 3


